---
title: "trying"
---

# Library Loading

```{r}
library(INLA)
library(IDPmisc)
require(rasterVis)
library(viridis)
library(latex2exp)
library(fields) #;library(imager);
library(lattice);require(latticeExtra) #;require(INLAutils)
require(classInt);require(reshape2)
library(FITSio)
library(MASS)

library(rmarkdown)

```

## Starry night or how to set a new color pallet

```{r}
Van_Gogh <- c("#263C8B","#4E74A6", "#BDBF78", "#BFA524", "#2E231F") 
colpal<-colorRampPalette(Van_Gogh)(100)
cutColor <- 100
zoom <- 1
```

1.  **Defining the Color Palette**: The `Van_Gogh` vector contains five hexadecimal color codes. These codes represent colors that resemble those used in Van Gogh's painting.

2.  **Color Palette Generation**: The `colorRampPalette()` function is then used to create a color palette (`colpal`) based on the colors defined in `Van_Gogh`. This palette is generated with 100 color values interpolated between the specified colors.

3.  **Color Cutoff**: The variable `cutColor` determines the number of color intervals to be used in the subsequent visualizations. This value is set to 100.

### The *cutoff* variable

```{r}
cutoff <- 0.9 #bit lower than minimum distance
```

It likely represents a threshold used to determine the range of influence or the validity of neighboring data points during the spatial interpolation process.

For example, it could be used to define a cutoff distance beyond which neighboring data points are considered too distant to significantly influence the interpolated value at a given location. Data points within this cutoff distance would have a stronger influence on the interpolation, while those beyond it would have a lesser impact.

Adjusting the cutoff value would change the spatial characteristics of the interpolation, potentially affecting the smoothness or detail of the resulting interpolated surface. A lower cutoff value would include more neighboring data points in the interpolation, resulting in a smoother but possibly less accurate surface. Conversely, a higher cutoff value would limit the influence of distant data points, resulting in a more localized but potentially more accurate interpolation.

# File and Directory Setup

```{r}
home <- "/home/dp/"
source(paste("./inla_fct.R",sep=''))
name <- "stavros"

dir <- paste("./first_results/",sep='')
file <- paste("galactic_center_masked_10",sep='')
outfile <- paste(file,"inla",sep='-')
eroutfile <- paste(file,"erinla",sep='-')

#read file
fits <- readFITS(file=paste(file,"fits",sep='.'))
img <- fits$imDat[,]
```

# Data Preparation

```{r}
subset_img <- img[1:40, 1:40]  # This will extract the top-left 20x20 portion of the img array
```

WHY ONLY THE TOP PART?????

```         
### x and y
dim <- dim(img)
x <- array(0,dim=dim)
y <- array(0,dim=dim)
for (i in 1:dim[1]){
    for (j in 1:dim[2]){
        x[i,j] <- i
        y[i,j] <- j
    }
}
```

???why not subset image???

```{r}
# Get dimensions of the img array
dims <- dim(img)

# Create x and y arrays using matrix indexing
x <- matrix(rep(1:dims[1], dims[2]), nrow = dims[1], ncol = dims[2])
y <- matrix(rep(1:dims[2], each = dims[1]), nrow = dims[1], ncol = dims[2])


##valid data
valid <- which(!(is.na(img)))
xsize <- dims[2]
ysize <- dims[1]
xfin <- xsize
yfin <- ysize


##normalize data
logimg = log10(img)

```

???? WHY X,Y, LOGIMG????\
function(tx, ty, tpar, tepar, weight=1, zoom = 1,... What is tx,ty,tpar,tepar???????????????????

```{r}
## INLA
#imginla <- nonparametric_inla(x[valid],y[valid],logimg[valid], xsize=xsize,ysize=ysize)

m_weights <- rep(1, nrow(cbind(x, y)))
imginla <- stationary_inla(x[valid],y[valid],logimg[valid],zoom=zoom,xsize=xsize,shape='none',xfin=xfin,yfin=yfin,ysize=ysize,cutoff=cutoff,tolerance=1e-6,restart=0L)
# placeholder for NaN = 0
imginla[is.nan(imginla$out[valid])] <- 0
logimg[is.nan(logimg[valid])] <- 0
```

```{r}

## PLOT
fj5_img <- classIntervals(c(logimg[valid],imginla$out[valid]), n = cutColor, style= "fisher")

inimg <- levelplot(imginla$image,xlim=c(0,ysize), ylim=c(0,xsize),col.regions=colpal,main = list(name,side=1,line=0.5,cex=1.4),ylab=list('y [pixels]',cex=1.5),cut=cutColor,at=fj5_img$brks,xlab=list('x [pixels]',cex=1.3))

outimg <- levelplot(imginla$out,xlim=c(0,ysize), ylim=c(0,xsize),
                    col.regions=colpal,xlab='x', ylab='y',cut=cutColor,at=fj5_img$brks)

fj5_erimg <- classIntervals(imginla$outsd[valid], n = cutColor, style= "fisher")

outsdimg <- levelplot(imginla$outsd,xlim=c(0,ysize), ylim=c(0,xsize),col.regions=colpal,xlab='x', ylab='y',cut=cutColor,at=fj5_erimg$brks)

save(x,y,logimg,imginla,file=paste(outfile,'Rdata',sep='.'))
writeFITSim(imginla$out,file=paste(outfile,'fits',sep='.'))
writeFITSim(imginla$outsd,file=paste(eroutfile,'fits',sep='.'))

png(filename=paste(outfile,'png',sep='.'))
c(inimg,outimg,outsdimg,layout=c(3,1))
dev.off()
```
